Programming Language Survey Paper on Haskell

### 2013-04-20 projects/term_paper/paper.tex
update

\subsection{Data Abstractions}
\subsubsection{Data Types}

Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values. Sub-data types for numbers exist to explicitly define characteristics of the type of number represented. For example, Haskell has two types of integers: Int and Integer. Int has the system-defined maximum integer size as its range while Integer’s ranged is only bound by the available amount of memory, and thus re used for arbitrary precision integers. Haskell also has two floating point types: Float and Double, where a Double has twice the floating point precision of a Float.

@@

>>>>

\subsection{Data Abstractions}
\subsubsection{Data Types}
Haskell includes many of the data types that are standard in most languages: Numbers, Characters, and Boolean values. Sub-data types for numbers exist to explicitly define characteristics of the type of number represented. For example, Haskell has two types of integers: Int and Integer. Int has the system-defined maximum integer size as its range while Integer’s ranged is only bound by the available amount of memory, and thus re used for arbitrary precision integers. Haskell also has two floating point types: Float and Double, where a Double has twice the floating point precision of a Float.

@@

Haskell also has a String data type. Although Strings are represented by double quotations, they are actually stored as a list of characters. Thus, when specificying a data type, String and [Char] are equivalent.
